Top Private Equity Firms with Larger Average Fund Sizes and Lower Internal Rate of Returns (IRRs) in the United States Give ESG a Higher Importance

### 2024-04-18 paper/paper.qmd
Model Summary Table

library(palmerpenguins)
library(here) 
library(arrow)
library(here)
library(gridExtra)
library(gtsummary)

@@

tbl_regression(esg_model)

modelsummary(esg_model)

>>>>

library(palmerpenguins)
library(here) 
library(arrow)
library(gridExtra)
library(gtsummary)

@@

tidy_model <- broom.mixed::tidy(esg_model)

tidy_model <- tidy_model %>%
  mutate(term = case_when(
    term == "(Intercept)"        ~ "Intercept",
    term == "Totalnumberoffunds" ~ "Total Number of Funds",
    term == "FundSize_Preqin"    ~ "Fund Size",
    term == "Sum_wirr_preqin"    ~ "IRR",
    term == "Staff_Count"        ~ "Staff",
    term == "Average_Fund_Size"  ~ "Average Fund Size",
    TRUE                         ~ term
  ))

kable(tidy_model, format = "markdown", 
      col.names = c("Term", "Estimate", "Std. Error"),
      digits = 3)
